AbxD01 Analysis

### 2015-01-30 abxD01_analysis.Rmd
going through results to tweak things

```{r, eval=FALSE}
file<-read.csv("~/Documents/Github/abxD01/Figure 3/abxD01.final.tx.2.subsample.allstreptitr.forlogscale.csv", header=T)
file<-file[file$expgroup!="1untrStrep",]
kruskal.test(file$Otu001 ~ file$expgroup)
kruskal.test(file$Otu003 ~ file$expgroup)
kruskal.test(file$Otu002 ~ file$expgroup)
kruskal.test(file$Otu005 ~ file$expgroup)
kruskal.test(file$Otu004 ~ file$expgroup)
kruskal.test(file$Otu014 ~ file$expgroup)
kruskal.test(file$Otu006 ~ file$expgroup)
kruskal.test(file$Otu007 ~ file$expgroup)
kruskal.test(file$Otu009 ~ file$expgroup)
kruskal.test(file$Otu015 ~ file$expgroup)
kruskal.test(file$Otu017 ~ file$expgroup)
kruskal.test(file$Other ~ file$expgroup)

>>>>

For comparison of the CFU's among titration groups: 
```{r, eval=FALSE}
file<-read.csv("~/Documents/Github/abxD01/Figure 3/abxD01.final.tx.2.subsample.allstreptitr.forlogscale.csv", header=T)
file<-file[file$expgroup!="1untrStrep",]
avgCD<-tapply(file$nextDayCFU, file$expgroup, mean)
strep_avgCD<-format(avgCD, scientific=TRUE, digits=2)
file$nextDayCFU <- log10(file$nextDayCFU+1)
#kruskal.test(file$nextDayCFU ~ file$expgroup)
# p < 0.0001
#strep_CFU_wilcox <- pairwise.wilcox.test(file$nextDayCFU, file$expgroup, p.adj="BH")
# all significantly different
strep.aov<-aov(file$nextDayCFU ~ file$expgroup)
anova(strep.aov)
#TukeyHSD(strep.aov)
strep_ttest <- pairwise.t.test(file$nextDayCFU, file$expgroup, p.adjust="BH")
# all significantly different

file<-read.csv("~/Documents/Github/abxD01/Figure 3/abxD01.final.tx.2.subsample.allceftitr.forlogscale.csv", header=T)
file<-file[file$expgroup!="1untrCef",]
avgCD<-tapply(file$nextDayCFU, file$expgroup, mean)
cef_avgCD<-format(avgCD, scientific=TRUE, digits=2)
file$nextDayCFU <- log10(file$nextDayCFU+1)
#kruskal.test(file$nextDayCFU ~ file$expgroup)
# p = 0.003
#cef_CFU_wilcox <- pairwise.wilcox.test(file$nextDayCFU, file$expgroup, p.adj="BH")
# mid and low dose not different, but high different than mid and low
#cef.aov<-aov(file$nextDayCFU ~ file$expgroup)
anova(cef.aov)
#TukeyHSD(cef.aov)
cef_ttest <- pairwise.t.test(file$nextDayCFU, file$expgroup, p.adjust="BH")
# all significantly different

file<-read.csv("~/Documents/Github/abxD01/Figure 3/abxD01.final.tx.2.subsample.allvanctitr.forlogscale.csv", header=T)
file<-file[file$expgroup!="1untrVanc",]
avgCD<-tapply(file$nextDayCFU, file$expgroup, mean)
vanc_avgCD<-format(avgCD, scientific=TRUE, digits=2)
file$nextDayCFU <- log10(file$nextDayCFU+1)
#kruskal.test(file$nextDayCFU ~ file$expgroup)
# p = 0.0016
#vanc_CFU_wilcox <- pairwise.wilcox.test(file$nextDayCFU, file$expgroup, p.adj="BH")
# mid and low dose not different, but high different than mid and low
vanc.aov<-aov(file$nextDayCFU ~ file$expgroup)
anova(vanc.aov)
#TukeyHSD(vanc.aov)
vanc_ttest <- pairwise.t.test(file$nextDayCFU, file$expgroup, p.adjust="BH")
# mid and low dose not different, but high different than mid and low

For comparisons between family-level phylotypes:
Performed inside abxD01.barcharts.xOTU.test.r
```{r, eval=FALSE}
file<-read.csv("~/Documents/Github/abxD01/Figure 3/abxD01.final.tx.2.subsample.allstreptitr.forlogscale.csv", header=T)
file<-file[file$expgroup!="1untrStrep",]
kruskal.test(file$Otu001 ~ file$expgroup)
kruskal.test(file$Otu003 ~ file$expgroup)
kruskal.test(file$Otu002 ~ file$expgroup)
kruskal.test(file$Otu005 ~ file$expgroup)
kruskal.test(file$Otu004 ~ file$expgroup)
kruskal.test(file$Otu014 ~ file$expgroup)
kruskal.test(file$Otu006 ~ file$expgroup)
kruskal.test(file$Otu007 ~ file$expgroup)
kruskal.test(file$Otu009 ~ file$expgroup)
kruskal.test(file$Otu015 ~ file$expgroup)
kruskal.test(file$Otu017 ~ file$expgroup)
kruskal.test(file$Other ~ file$expgroup)
